Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
trying another thing
anonymize readme file

---
title: "Hidden Talents Multiverse Analysis"
output: md_document
---

@@

This repository contains data, code, and (some) output for a working manuscript by Young, Frankenhuis, and Ellis (in progress).

>>>>

---
title: "Hidden Talents Multiverse Analysis"
output: github_document
---

@@

This repository contains data, code, and (some) output for a working manuscript.
